Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL. 
Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

@@

\begin{enumerate}
\item
\emph{Data quality can be significantly improved when suitable constraint languages are developed enabling to define 
constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way. Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only be specified by SPARQL.}
\item
\emph{The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.}  
\item
\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations. This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
\item
\emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
There is a significant demand for languages that support the expression of SPARQL Based constraints causing 94\% of all violations.}
\end{enumerate}

>>>>

We published by today 81 constraint types that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL. 
Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

@@

\begin{enumerate}
\item
\emph{Data quality can be significantly improved when suitable constraint languages are developed enabling to define 
constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way. Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only be specified by SPARQL.}
\item
\emph{As only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, data quality is high for all vocabularies with regard to their formal specifications.}  
\item
\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations. This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
\item
\emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
There is a significant demand for languages that support the expression of SPARQL Based constraints causing 94\% of all violations.}
\end{enumerate}
